Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-19 manuscript/manuscript.tex
Update neuquen basin text in manuscript

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/neuquen-basin.pdf}
\caption{
    Gravitational effects of the Nequ\'en sedimentary basin modelled
    using tesseroids with an exponential density function of depth.
    (a) Topography of the Neuqu\'en Basin (in km) and its location in South America,
    (b) thickness of the sedimentary basin \citep[in meters;][]{Heine2007},
    (c) the exponential density function used to model the basin
        (depth in km and density in kg/m$^3$),
    (d)-(l) computed gravitational fields: potential $V$ (in J/kg), gradient
    components $g_x$, $g_y$ and $g_z$ (in mGal), and Marussi tensor components
    (in Eötvös), calculated at 50km of height over the ellipsoid.
}
\label{fig:neuquen-basin}
\end{figure*}

The thickness of the sediment pack was digitized from \citet{Heine2007} on a regular
grid with a resolution of 0.05$^\circ$ on both longitude and latitude directions
(Fig.~\ref{fig:neuquen-basin}b).
We created a tesseroid model of the sediment pack by placing a
$0.05^\circ \times 0.05^\circ$ tesseroid on each node of the grid.
The top of each tesseroid was fixed at 0 m depth and the bottom at corresponding
thickness of the basin.

We must also define a density function for the tesseroid model.
\citet{Sigismondi2012} measured a minimum and maximum density contrast for
the Neuqu\'en basin of -412kg/m$^3$ and -275kg/m$^3$, respectively.
We have chosen an exponential density variation (Eq.~\ref{eq:density-exp}) that assumes
the minimum value on the top surface and the maximum at 5858m depth (the thickest part
of the basin), with a value of $b$ equal to 2km.
This density function can be seen on Fig.~\ref{fig:neuquen-basin}c.

Finally, we computed the gravitational potential $V$, gradient components $g_x$,
$g_y$ and $g_z$, and the Marussi tensor components $g_{xx}$, $g_{xy}$,
$g_{xz}$, $g_{yy}$, and $g_{zz}$ on a computation grid of $159\times163$ nodes
($0.05^\circ$ spacing on both longitude and latitude) at a 50km height over the
reference ellipsoid.
The resulting fields can be seen in Fig.~\ref{fig:neuquen-basin}d-l.
We have excluded the other components of the Marussi tensor from the
Fig.~\ref{fig:neuquen-basin}, although they can be found in the online repository.

>>>>

\begin{figure}
\centering
\iftwocol{
\includegraphics[width=\linewidth]{figures/neuquen-basin-densities.pdf}
}{
\includegraphics[width=0.5\linewidth]{figures/neuquen-basin-densities.pdf}
}
\caption{
    Linear and exponential densities used to compute the gravitational fields generated
    by a tesseroid model of the Neuquen sedimentary basin.
    The height is defined above the mean Earth radius, and its axis is spanned between
    the deepest and the highest point of the basin.
}
\label{fig:neuquen-basin-densities}
\end{figure}

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/neuquen-basin.pdf}
\caption{
    Gravitational effects of the Nequ\'en sedimentary basin modelled
    using tesseroids with an exponential density function of depth.
    (a) Topography of the Neuqu\'en Basin (in km) and its location in South America,
    (b) thickness of the sedimentary basin \citep[in meters;][]{Heine2007},
    (c) resulting gravitational potential $V$,
    (d) resulting vertical component of the gradient ($g_z$),
    calculated at 10km of height over the mean Earth radius.
}
\label{fig:neuquen-basin}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=\linewidth]{figures/neuquen-basin-diffs.pdf}
\caption{
    Differences between the gravitational fields generated by the tesseroid model of the
    Neuquen basin with an exponential density contrast and with a homogenenous and
    linear density variation.
    (a)-(b) Differences on $V$ and $g_z$ between the exponential density model and the
    homogenenous density one,
    (c)-(f) differences on $V$ and $g_z$ between the exponential density model and the
    linear density one,
    calculated at 10km of height over the mean Earth radius.
}
\label{fig:neuquen-basin-diffs}
\end{figure*}

The thickness of the sediment pack was digitized from \citet{Heine2007} on a regular
grid with a resolution of 0.05$^\circ$ on both longitude and latitude directions
(Fig.~\ref{fig:neuquen-basin}b).
We created a tesseroid model of the sediment pack by placing a
$0.05^\circ \times 0.05^\circ$ tesseroid on each node of the grid.
The top of each tesseroid was fixed at the median of the topography of the basin
(845~m above mean Earth radius) and the bottom at corresponding thickness of the basin.

We must also define a density function for the tesseroid model.
\citet{Sigismondi2012} measured a minimum and maximum density contrast for
the Neuqu\'en basin of -412kg/m$^3$ and -275kg/m$^3$, respectively.
We have chosen an exponential density variation (Eq.~\ref{eq:density-exp}) that assumes
the minimum value on the top surface and the maximum at 5014m depth (the thickest part
of the basin), with a value of $b$ equal to 3.
This density variation is in agreement with the ones used by
This density function can be seen on Fig.~\ref{fig:neuquen-basin-densities}.

Finally, we computed the gravitational potential $V$ and the vertical component of the
gradient ($g_z$) on a computation grid of $159\times163$ nodes ($0.05^\circ$ spacing on
both longitude and latitude) at a 10km height over the mean Earth radius.
The resulting fields can be seen in Fig.~\ref{fig:neuquen-basin}c-d.
Moreover, we computed the differences between these fields and the ones generated by the
same model but now with a constant density as the mean value between -412kg/m$^3$ and
-275kg/m$^3$, and a linear density that assumes these two values on the highest and the
deepest point of the basin, respectively (Fig.~\ref{fig:neuquen-basin-densities}).
Fig.~\ref{fig:neuquen-basin-diffs}a-b and Fig.~\ref{fig:neuquen-basin-diffs}c-d show the
differences with the constant and the linear density, respectively
